### 2022-11-28 dissertation/chapters/01-introduction.tex
🚧 (final-review): Chapter 7 WIP

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based meta-heuristics in real-valued dynamic optimization. However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.

@@

      \item \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of heuristics and meta-heuristics that have been used to train \acp{FFNN}. A literature study is done to provide details on the search behaviours, application and implementation of each heuristic in the context of training \acp{FFNN}.

>>>>

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization. However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.

@@

      \item \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of heuristics and \acp{MH} that have been used to train \acp{FFNN}. A literature study is done to provide details on the search behaviours, application and implementation of each heuristic in the context of training \acp{FFNN}.

### 2022-11-28 dissertation/chapters/03-heuristics.tex
🚧 (final-review): Chapter 7 WIP

Many different techniques have been used to train \acp{FFNN}~\cite{ref:kingma:2014}. Finding the best technique to use to train a \acs{FFNN} has been shown to be problem dependent in many cases~\cite{ref:kheiri:2017}. Every technique has its characteristics, constraints, advantages and disadvantages. At the time of writing, the majority of work that is published around the training of \acp{FFNN}, involves the use of gradient-based techniques~\cite{ref:nel:2021}. Gradient-based techniques are not without flaws and can, for example, yield slow convergence or get trapped in local optima~\cite{ref:mingguang:2009}. Other techniques have also been used to successfully train \acp{FFNN}, including meta-heuristics such as \acf{PSO}~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE}~\cite{ref:espinal:2011} and \acfp{GA}~\cite{ref:gupta:1999}.

@@

This section aims to introduce the concept of \acp{MH}, with focus on population-based meta-heuristics. Three well known \acp{MH}, that have been shown to train \acs{FFNN}, are presented. These meta-heuristics include \acf{PSO}, \acf{DE} and \acfp{GA}.~\citeauthor{ref:carvalho:2006}~\cite{ref:carvalho:2006} compared various \acs{PSO} variants for training \acp{FFNN}.~\citeauthor{ref:espinal:2011}~\cite{ref:espinal:2011} compared \acs{DE} and \acs{PSO} when applied to \acs{FFNN} training and~\citeauthor{ref:gupta:1999}~\cite{ref:gupta:1999} compared \acs{BP} to a \acs{GA} for training \acp{FFNN}.

>>>>

Many different techniques have been used to train \acp{FFNN}~\cite{ref:kingma:2014}. Finding the best technique to use to train a \acs{FFNN} has been shown to be problem dependent in many cases~\cite{ref:kheiri:2017}. Every technique has its characteristics, constraints, advantages and disadvantages. At the time of writing, the majority of work that is published around the training of \acp{FFNN}, involves the use of gradient-based techniques~\cite{ref:nel:2021}. Gradient-based techniques are not without flaws and can, for example, yield slow convergence or get trapped in local optima~\cite{ref:mingguang:2009}. Other techniques have also been used to successfully train \acp{FFNN}, including \acp{MH} such as \acf{PSO}~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE}~\cite{ref:espinal:2011} and \acfp{GA}~\cite{ref:gupta:1999}.

@@

This section aims to introduce the concept of \acp{MH}, with focus on population-based meta-heuristics. Three well known \acp{MH}, that have been shown to train \acs{FFNN}, are presented. These \acp{MH} include \acf{PSO}, \acf{DE} and \acfp{GA}.~\citeauthor{ref:carvalho:2006}~\cite{ref:carvalho:2006} compared various \acs{PSO} variants for training \acp{FFNN}.~\citeauthor{ref:espinal:2011}~\cite{ref:espinal:2011} compared \acs{DE} and \acs{PSO} when applied to \acs{FFNN} training and~\citeauthor{ref:gupta:1999}~\cite{ref:gupta:1999} compared \acs{BP} to a \acs{GA} for training \acp{FFNN}.

### 2022-11-28 dissertation/chapters/04-hyper-heuristics.tex
🚧 (final-review): Chapter 7 WIP

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based meta-heuristics in real-valued dynamic optimization. Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training. The following section provides a framework for \acs{HH} classification.

>>>>

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization. Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training. The following section provides a framework for \acs{HH} classification.

### 2022-11-28 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (final-review): Chapter 7 WIP

      \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \acs{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself. Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as meta-heuristics.

>>>>

      \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \acs{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself. Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as \acp{MH}.
